An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-23 uai2017/paper.tex
update figures and results

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 181, more than an order of
magnitude better compared to the other two methods (averages are 13511 and
73011). Sizes correspond to the running times of the methods, excluding the
likelihood computation of all data points for {\sc MHSubLhd}, which would
drastically increase running time.

>>>>

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 213, more than an order of
magnitude better compared to the other two methods (averages are 11962 and
63408). Sizes correspond to the running times of the methods, excluding the
likelihood computation of all data points for {\sc MHSubLhd}, which would
drastically increase running time.
